TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
uji coba
gambar

---
title: "MENYELESAIKAN POLINOMIAL DENGAN NUMPY"
subtitle: | 
    | Tugas Mata Kuliah SK5003 Pemrograman dalam Sains
    | Numpy Python 3
author: | 
    | Mohammad Rizka Fadhli (Ikang)
    | 20921004@mahasiswa.itb.ac.id
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: false
    toc: false
    fig_width: 7
    fig_height: 4
    fig_caption: true
    highlight: zenburn
    dev: png
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{hal \thepage}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/209_ITB/Semester I/Pemrograman dalam Sains/Minggu VIII")
rm(list=ls())
library(dplyr)
library(ggplot2)
```

@@

Develop a Python program to evaluate polynomial function $y = x^4 + 4x^2 +7$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the graph.

@@

@@

# TASK 4

Develop a Python program to solve the polynomial function $y = x^4 + 4x^2 + 7$.

>>>>

---
title: "TUGAS POLINOMIAL CHAPTER 15"
subtitle: | 
    | Tugas Mata Kuliah SK5003 Pemrograman dalam Sains
    | Numpy Python 3
author: | 
    | Mohammad Rizka Fadhli (Ikang)
    | 20921004@mahasiswa.itb.ac.id
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: false
    toc: false
    fig_width: 7
    fig_height: 4
    fig_caption: true
    highlight: zenburn
    dev: png
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{20921004@mahasiswa.itb.ac.id}
- \fancyfoot[LE,RO]{hal \thepage}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())
library(dplyr)
library(ggplot2)

gambar_fx = function(f,a,b,delta){
  temp = data.frame(
    x = seq(a,b,by = delta)
  ) %>% 
    mutate(y = f(x)) %>% 
    filter(!is.nan(y))
  subtitle = paste0("Pada selang [",a,",",b,"]")
  caption = "Digambar dengan R\nikanx101.com"
  temp %>% 
    ggplot(aes(x,y)) +
    geom_line(color = "steelblue") +
    theme_minimal() +
    labs(title = "Grafik f(x)",
         subtitle = subtitle,
         caption = caption)

}

```

@@

__15.1__ Develop a Python program to evaluate polynomial function $y = x^4 + 4x^2 +7$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the graph.

__15.4__ Develop a Python program to solve the polynomial function $y = x^4 + 4x^2 + 7$.

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE}
f = function(x){x^4 + 4*x^2 + 7}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@
